
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass{Dissertate}

\begin{document}

% the front matter
\input{frontmatter/personalize}
\maketitle
%\copyrightpage

% Force all citations to show up in references
\nocite{*}

\setstretch{1.2}
\abstractpage
\tableofcontents
%\listoffigures
\dedicationpage
\acknowledgments

\doublespacing

% include each chapter...
\setcounter{chapter}{-1}  % start chapter numbering at 0

\chapter{Introduction}
\label{introduction}

Much of the recent history of genome editing consists of building the site-specificity of a nuclease through engineered protein-DNA interactions. Though this technique has proven effective and useful, as seen in the examples of Zinc-Finger Nucleases (ZFNs) and Transcription Activator-Like Effector Nucleases (TALENs), these platforms are difficult to use because of the complexity of programming protein-DNA specificity.
In recent years, the CRISPR-Cas bacterial immune system has been extensively used as a genome engineering alternative that relies on RNA-DNA complementarity as the homing interaction that guides the specificity of the Cas9 nuclease. The ease of using such a platform to cleave specific sites in the genome simply by choosing a guide RNA sequence complementary to the target sequence has lead to an explosion in its use, with enormous amounts of interest and capital being contributed to the investigation of further development and application of this technology (Doudna and Charpentier \textit{et al.} 2014).

\chapter{Background}
\label{Background}

\section{Test Section}
\subsection{Test Subsection}
Much of the recent history of genome editing consists of building the site-specificity of a nuclease through engineered protein-DNA interactions. Though this technique has proven effective and useful, as seen in the examples of Zinc-Finger Nucleases (ZFNs) and Transcription Activator-Like Effector Nucleases (TALENs), these platforms are difficult to use because of the complexity of programming protein-DNA specificity.
In recent years, the CRISPR-Cas bacterial immune system has been extensively used as a genome engineering alternative that relies on RNA-DNA complementarity as the homing interaction that guides the specificity of the Cas9 nuclease. The ease of using such a platform to cleave specific sites in the genome simply by choosing a guide RNA sequence complementary to the target sequence has lead to an explosion in its use, with enormous amounts of interest and capital being contributed to the investigation of further development and application of this technology (Doudna and Charpentier \textit{et al.} 2014).

%\include{chapters/introduction}
%\include{chapters/chapter1}
%\include{chapters/chapter2}
%\include{chapters/chapter3}
%\include{chapters/conclusion}
%\begin{appendices}
%    \include{chapters/appendixA}
%\end{appendices}
%
%\setstretch{1.2}
%
% the back matter
\clearpage
\bibliography{VVT_Thesis_References}
\addcontentsline{toc}{chapter}{References}
\bibliographystyle{apalike2}

%\include{endmatter/colophon}

\end{document}
