% the acknowledgments section

First I would like to thank the machines, specifically the espresso machines of Starbucks, for making this thesis possible. They may not be artificially intelligent, but I certainly wouldn't be intelligent without their support. People have been helpful as well. My advisor Stuart Shieber welcomed me into this field and provided invaluable advice and intellectual support throughout the entire project. Krzysztof Gajos supplied crucial feedback on the design of the website and encouraged me to pursue this crazy idea. Sasha Rush cemented my passion for AI and NLP with his two courses on the subjects, and forgave me when I invited him to a cancelled faculty dinner. Many friends and family helped test-drive the website and proofread this document. I am especially indebted to Joshua Leifer, Manik Kuchroo, Martin Carlino, Matthew Disler, Yuning Zhang, Priya Menon, Jack Dent, Erin Masatsugu, Sundar Solai, Kevin Yang, Ankit Gupta, and Madhu Vijay. My parents and Hannah Blumberg also provided feedback on the entire thesis draft, but they deserve separate thank-yous for providing the even more valuable emotional support throughout all the ups and downs of the thesis experience. Here's another sentence thanking Hannah Blumberg, since she deserves two (and many more). Finally, I would like to thank all the players of the web implementation of Luna: your creative and amusing questions and responses sustained me throughout the stressful experience of launching a website.